Verification and Synthesis of Embedded Systems: \\ Advances and Challenges

### 2017-01-01 paper.tex
Added a new reference related to DepthK

There are several invariant-generation algorithms that discover linear and polynomial relations among integer and real variables, in order to provide loop invariants and also discover the memory ``shape'', in programming languages with pointers~\cite{pips:2013,Henry:2012}. The current literature also reports successful applications of \textit{k}-induction based verification algorithms for hardware and software systems, using invariant generation and strengthening, mostly based on interval analysis.

Novel verification algorithms for proving correctness of (a large set of) C programs, by mathematical induction, in a completely automatic way ({\it i.e.}, users do not need to provide the loop invariant) were recently proposed~\cite{Gadelha15,Beyer15,Brain15,Rocha15,Kinductor}. Additionally, \textit{k}-induction based verification was also applied to ensure that (restricted) C programs (1) do not contain violations related to data races~\cite{Donaldson10}, considering the Cell BE processor, and (2) do respect time constraints, which are specified during the system design phase~\cite{EenS03}. Apart from that, the \textit{k}-induction algorithm is also a well-established technique in hardware verification, where it is easily applied, due to the monolithic transition relation present in such designs~\cite{EenS03,Sheera00,GrosseLD09}.

@@

% use section* for acknowledgment
\section*{Acknowledgment}

%The authors would like to thank...
The authors thank M. Dangl for reviewing a draft version of this paper.~This research was supported by CNPq $475647$/$2013$-$0$ grant.

@@

%8
\bibitem{Abate17}
Abate A., Bessa I., Cattaruzza D., Cordeiro L., David C., Kesseli P., Kroening D.:
\newblock {\em Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants}.
\newblock In: 20th International Conference on Hybrid Systems: Computation and Control, 2017 (to appear).

@@

%27
\bibitem{Rocha15}
Rocha H., Ismail H., Cordeiro L., Barreto R.:
\newblock {\em Model Checking Embedded C Software using \textit{k}-Induction and Invariants.}
\newblock V Brazilian Symposium on Computing Systems Engineering, pp. 90--95, 2015.

@@

%29
\bibitem{Donaldson10}
Donaldson A., Kroening D., R{\"{u}}mmer P.:
\newblock {\em {SCRATCH}: A Tool for Automatic Analysis of {DMA} Races.}
\newblock In: ACM Symposium on Principles and Practice of Parallel Programming. ACM, pp. 311--312, 2011.

%30
\bibitem{GrosseLD09}
Gro{\ss}e D., Le H., Drechsler R.:
\newblock {\em Induction-based Formal Verification of {SystemC TLM} Designs.}
\newblock In: International Workshop on Microprocessor Test and Verification, pp. 101--106, 2009.

%31
\bibitem{Behrend15}
Behrend J., Lettnin D., Gruenhage A., Ruf J., Kropf T., Rosenstiel W.:
\newblock {\em Scalable and Optimized Hybrid Verification of Embedded Software}. 
\newblock In: J. Electronic Testing 31(2): pp. 151--166, 2015.

%32
\bibitem{dsv_spin2015}
Ismail H., Bessa I., Cordeiro L., Lima Filho E., Chaves Filho J.:
\newblock {\em DSVerifier: A Bounded Model Checking Tool for Digital Systems}. 
\newblock In: International SPIN Symposium on Model Checking of Software, LNCS 9232, pp. 126--131, 2015.

%33
\bibitem{Lettnin09}
Lettnin D., Nalla P. K., Behrend J., Ruf J., Gerlach J., Kropf T., Rosenstiel W., Sch{\"o}nknecht V., Reitemeyer S.:
\newblock {\em Semiformal Verification of Temporal Properties in Automotive Hardware Dependent Software}. 
\newblock In: Design, Automation and Test in Europe, pp. 1214--1217, 2009.

%34
\bibitem{Beyer14}
D.~Beyer 
\newblock {Status report on software verification - (competition summary {SV-COMP})}. 
\newblock In: Tools and Algorithms for the Construction and Analysis of Systems, LNCS 8413, pp. 373--388, 2014.

%35
\bibitem{BeyerSVCOMP15}
D.~Beyer:
\newblock {\em Software Verification and Verifiable Witnesses - (Report on SV-COMP 2015).} 
\newblock In: Tools and Algorithms for the Construction and Analysis of Systems, LNCS 9035, pp. 401-416, 2015.

%36
\bibitem{Inverso14}
Inverso O., Tomasco E., Fischer B., La Torre S., Parlato G.:
\newblock {\em Bounded Model Checking of Multi-threaded C Programs via Lazy Sequentialization.}
\newblock In: International Conference on Computer-Aided Verification, LNCS 8559, pp. 585-602, 2014.

%37
\bibitem{ECBS13}
Ramalho M., Lopes M., Sousa F., Marques H., Cordeiro L., Fischer B.:
\newblock {\em {SMT-Based Bounded Model Checking of C++ Programs} }.
\newblock In: International Conference on Engineering of Computer-Based Systems, pp. 147--156, 2013.

%38
\bibitem{Pereira15}
Pereira P.  Albuquerque H., Marques H., Silva I., Carvalho C., Santos V., Ferreira R., Cordeiro L.: 
\newblock {\em Verifying CUDA Programs using SMT-Based Context-Bounded Model Checking.} 
\newblock In: ACM Symposium on Applied Computing, Software Verification and Testing Track, pp. 1648-1653, 2016.

%39
\bibitem{Sousa15}
Sousa F., Cordeiro L., Lima Filho E.: 
\newblock {\em { Bounded Model Checking of C++ Programs Based on the Qt Framework.}} 
\newblock In: Global Conference on Consumer Electronics, pp. 179--180, 2015.

%40
\bibitem{morse15}
J.~Morse.
\newblock {\em {Expressive and Efficient Bounded Model Checking of Concurrent Software}}.
\newblock {University of Southampton, PhD Thesis}, 2015.

%41
\bibitem{civl15}
Zheng M, Rogers M, Luo Z, Dwyer M, Siegel S.
\newblock {\em{{CIVL}: Formal Verification of Parallel Programs}}.
\newblock In: International Conference on Automated Software Engineering, pp. 830--835, 2015.

%42
\bibitem{Grumberg05}
Grumberg O., Lerda F., Strichman O., Theobald M.:
\newblock {\em { Proof-guided underapproximation-widening for multi-process systems.}} 
\newblock In: Symposium on Principles of Programming Languages, pp. 122--131, 2005.

%43
\bibitem{McMillan11}
K.~McMillan:
\newblock {\em {Widening and Interpolation.}} 
\newblock In: International Symposium on Static Analysis, LCNS 6887, pp. 1, 2011.

%44
\bibitem{esbmc_controller}
Bessa I., Abreu R., Cordeiro L., Filho J.:
\newblock {\em {SMT-Based Bounded Model Checking of Fixed-Point Digital Controllers)}.}
\newblock In: Annual Conference of the Industrial Electronics Society, pp. 295--301, 2014.

%45
\bibitem{esbmc_filter}
Abreu R., Cordeiro L., Filho E.:
\newblock {\em {Verifying Fixed-Point Digital Filters using SMT-Based Bounded Model Checking}.}
\newblock In: XXXI Brazilian Symposium on Telecommunications, 2013.
\newblock http://dx.doi.org/10.14209/sbrt.2013.57

%46
\bibitem{JMorse15}
Morse J., Cordeiro L., Nicole D., Fischer B.:
\newblock {\em {Model Checking LTL Properties over ANSI-C Programs with Bounded Traces.}} 
\newblock In: Software and System Modeling 14(1): pp. 65--81, 2015.

%47
\bibitem{Bessa16}
Bessa I., Ismail H., Cordeiro L., Chaves Filho J.:
\newblock {\em { Verification of Fixed-Point Digital Controllers Using Direct and Delta Forms Realizations.}} 
\newblock In: Design Automation for Embedded Systems (to appear), 2016.

%48
\bibitem{MorseCNF13}
Morse J., Cordeiro L., Nicole D., Fischer B.:
\newblock {\em Handling unbounded loops with {ESBMC} 1.20.}
\newblock In: Tools and Algorithms for the Construction and Analysis of
  Systems. LNCS 7795, Springer Berlin Heidelberg, pp. 619--622, 2013.

%49
\bibitem{MorseRCN014}
Morse J., Ramalho M., Cordeiro L., Nicole D., Fischer B.:
\newblock {\em {ESBMC} 1.22.}
\newblock In: Tools and Algorithms for the Construction and Analysis of
  Systems. LNCS 8413, Springer Berlin Heidelberg, pp. 405--407, 2014.

%50
\bibitem{KahlonWG09}
Kahlon V., Wang C., Gupta A.:
\newblock {\em{Monotonic Partial Order Reduction: An Optimal Symbolic Partial Order Reduction Technique}}.
\newblock In: International Conference on Computer-Aided Verification, LNCS 5643, pp. 398--413, 2009.

%51
\bibitem{Alves15}
Alves E. , Cordeiro L., Lima Filho E.:
\newblock {\em{ Fault Localization in Multi-Threaded C Programs using Bounded Model Checking}}. 
\newblock In: Brazilian Symposium on Computing Systems Engineering, pp. 96-101, 2015.

%52
\bibitem{Garcia16}
Garcia M. , Sousa F., Cordeiro, L., Lima Filho E.: 
\newblock {\em{ ESBMC$^{QtOM}$: A Bounded Model Checking Tool to Verify Qt Applications}}. 
\newblock In: International SPIN symposium on Model Checking of Software (to appear), 2016.

%53
\bibitem{BeyerW15}
Beyer D., Dangl M., Dietsch D., Heizmann M., Stahlbauer A.:
\newblock {\em{ Witness validation and stepwise testification across software verifiers}}. 
\newblock In: ESEC/SIGSOFT Foundations of Software Engineering, pp. 721--733, 2015.

%54
\bibitem{RochaIFM12}
Rocha H., Barreto R., Cordeiro L., Dias Neto A.:
\newblock {\em{ Understanding Programming Bugs in ANSI-C Software Using Bounded Model Checking Counter-Examples}}. 
\newblock In: International Conference on Integrated Formal Methods, LNCS 7321, pp. 128-142, 2012.

>>>>

There are several invariant-generation algorithms that discover linear and polynomial relations among integer and real variables, in order to provide loop invariants and also to discover the memory ``shape'', in programming languages with pointers~\cite{pips:2013,Henry:2012}. The current literature also reports successful applications of \textit{k}-induction based verification algorithms for hardware and software systems, using invariant generation and strengthening, mostly based on interval analysis.

Novel verification algorithms for proving correctness of (a large set of) C programs, by mathematical induction, in a completely automatic way ({\it i.e.}, users do not need to provide the loop invariant) were recently proposed~\cite{Gadelha15,Beyer15,Brain15,Rocha15,Kinductor,Rocha17}. Additionally, \textit{k}-induction based verification was also applied to ensure that (restricted) C programs (1) do not contain violations related to data races~\cite{Donaldson10}, considering the Cell BE processor, and (2) do respect time constraints, which are specified during the system design phase~\cite{EenS03}. Apart from that, the \textit{k}-induction algorithm is also a well-established technique in hardware verification, where it is easily applied, due to the monolithic transition relation present in such designs~\cite{EenS03,Sheera00,GrosseLD09}.

@@

% use section* for acknowledgment
%\section*{Acknowledgment}

%The authors would like to thank...
%The authors thank M. Dangl for reviewing a draft version of this paper.~This research was supported by CNPq $475647$/$2013$-$0$ grant.

@@

%8
\bibitem{Abate17}
Abate A., Bessa I., Cattaruzza D., Cordeiro L., David C., Kesseli P., Kroening D.:
\newblock {\em Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants}.
\newblock In: 20th ACM International Conference on Hybrid Systems: Computation and Control, 2017 (to appear).

@@

%27
\bibitem{Rocha15}
Rocha H., Ismail H., Cordeiro L., Barreto R.:
\newblock {\em Model Checking Embedded C Software using \textit{k}-Induction and Invariants.}
\newblock In: V Brazilian Symposium on Computing Systems Engineering, pp. 90--95, 2015.

@@

%29
\bibitem{Rocha17}
Rocha, W., Rocha, H., Ismail H., Cordeiro, L., Fischer, B.:
\newblock {\em DepthK: A \textit{k}-Induction Verifier Based on Invariant Inference for C Programs}. 
\newblock In: International Conference on Tools and Algorithms for the Construction and Analysis of Systems, 2017 (to appear).

%30
\bibitem{Donaldson10}
Donaldson A., Kroening D., R{\"{u}}mmer P.:
\newblock {\em {SCRATCH}: A Tool for Automatic Analysis of {DMA} Races.}
\newblock In: ACM Symposium on Principles and Practice of Parallel Programming. ACM, pp. 311--312, 2011.

%31
\bibitem{GrosseLD09}
Gro{\ss}e D., Le H., Drechsler R.:
\newblock {\em Induction-based Formal Verification of {SystemC TLM} Designs.}
\newblock In: International Workshop on Microprocessor Test and Verification, pp. 101--106, 2009.

%32
\bibitem{Behrend15}
Behrend J., Lettnin D., Gruenhage A., Ruf J., Kropf T., Rosenstiel W.:
\newblock {\em Scalable and Optimized Hybrid Verification of Embedded Software}. 
\newblock In: J. Electronic Testing 31(2): pp. 151--166, 2015.

%33
\bibitem{dsv_spin2015}
Ismail H., Bessa I., Cordeiro L., Lima Filho E., Chaves Filho J.:
\newblock {\em DSVerifier: A Bounded Model Checking Tool for Digital Systems}. 
\newblock In: International SPIN Symposium on Model Checking of Software, LNCS 9232, pp. 126--131, 2015.

%34
\bibitem{Lettnin09}
Lettnin D., Nalla P. K., Behrend J., Ruf J., Gerlach J., Kropf T., Rosenstiel W., Sch{\"o}nknecht V., Reitemeyer S.:
\newblock {\em Semiformal Verification of Temporal Properties in Automotive Hardware Dependent Software}. 
\newblock In: Design, Automation and Test in Europe, pp. 1214--1217, 2009.

%35
\bibitem{Beyer14}
D.~Beyer 
\newblock {Status report on software verification - (competition summary {SV-COMP})}. 
\newblock In: Tools and Algorithms for the Construction and Analysis of Systems, LNCS 8413, pp. 373--388, 2014.

%36
\bibitem{BeyerSVCOMP15}
D.~Beyer:
\newblock {\em Software Verification and Verifiable Witnesses - (Report on SV-COMP 2015).} 
\newblock In: Tools and Algorithms for the Construction and Analysis of Systems, LNCS 9035, pp. 401-416, 2015.

%37
\bibitem{Inverso14}
Inverso O., Tomasco E., Fischer B., La Torre S., Parlato G.:
\newblock {\em Bounded Model Checking of Multi-threaded C Programs via Lazy Sequentialization.}
\newblock In: International Conference on Computer-Aided Verification, LNCS 8559, pp. 585-602, 2014.

%38
\bibitem{ECBS13}
Ramalho M., Lopes M., Sousa F., Marques H., Cordeiro L., Fischer B.:
\newblock {\em {SMT-Based Bounded Model Checking of C++ Programs} }.
\newblock In: International Conference on Engineering of Computer-Based Systems, pp. 147--156, 2013.

%39
\bibitem{Pereira15}
Pereira P.  Albuquerque H., Marques H., Silva I., Carvalho C., Santos V., Ferreira R., Cordeiro L.: 
\newblock {\em Verifying CUDA Programs using SMT-Based Context-Bounded Model Checking.} 
\newblock In: ACM Symposium on Applied Computing, Software Verification and Testing Track, pp. 1648-1653, 2016.

%40
\bibitem{Sousa15}
Sousa F., Cordeiro L., Lima Filho E.: 
\newblock {\em { Bounded Model Checking of C++ Programs Based on the Qt Framework.}} 
\newblock In: Global Conference on Consumer Electronics, pp. 179--180, 2015.

%41
\bibitem{morse15}
J.~Morse.
\newblock {\em {Expressive and Efficient Bounded Model Checking of Concurrent Software}}.
\newblock {University of Southampton, PhD Thesis}, 2015.

%42
\bibitem{civl15}
Zheng M, Rogers M, Luo Z, Dwyer M, Siegel S.
\newblock {\em{{CIVL}: Formal Verification of Parallel Programs}}.
\newblock In: International Conference on Automated Software Engineering, pp. 830--835, 2015.

%43
\bibitem{Grumberg05}
Grumberg O., Lerda F., Strichman O., Theobald M.:
\newblock {\em { Proof-guided underapproximation-widening for multi-process systems.}} 
\newblock In: Symposium on Principles of Programming Languages, pp. 122--131, 2005.

%44
\bibitem{McMillan11}
K.~McMillan:
\newblock {\em {Widening and Interpolation.}} 
\newblock In: International Symposium on Static Analysis, LCNS 6887, pp. 1, 2011.

%45
\bibitem{esbmc_controller}
Bessa I., Abreu R., Cordeiro L., Filho J.:
\newblock {\em {SMT-Based Bounded Model Checking of Fixed-Point Digital Controllers)}.}
\newblock In: Annual Conference of the Industrial Electronics Society, pp. 295--301, 2014.

%46
\bibitem{esbmc_filter}
Abreu R., Cordeiro L., Filho E.:
\newblock {\em {Verifying Fixed-Point Digital Filters using SMT-Based Bounded Model Checking}.}
\newblock In: XXXI Brazilian Symposium on Telecommunications, 2013.
\newblock http://dx.doi.org/10.14209/sbrt.2013.57

%47
\bibitem{JMorse15}
Morse J., Cordeiro L., Nicole D., Fischer B.:
\newblock {\em {Model Checking LTL Properties over ANSI-C Programs with Bounded Traces.}} 
\newblock In: Software and System Modeling 14(1): pp. 65--81, 2015.

%48
\bibitem{Bessa16}
Bessa I., Ismail H., Cordeiro L., Chaves Filho J.:
\newblock {\em { Verification of Fixed-Point Digital Controllers Using Direct and Delta Forms Realizations.}} 
\newblock In: Design Automation for Embedded Systems (to appear), 2016.

%49
\bibitem{MorseCNF13}
Morse J., Cordeiro L., Nicole D., Fischer B.:
\newblock {\em Handling unbounded loops with {ESBMC} 1.20.}
\newblock In: Tools and Algorithms for the Construction and Analysis of
  Systems. LNCS 7795, Springer Berlin Heidelberg, pp. 619--622, 2013.

%50
\bibitem{MorseRCN014}
Morse J., Ramalho M., Cordeiro L., Nicole D., Fischer B.:
\newblock {\em {ESBMC} 1.22.}
\newblock In: Tools and Algorithms for the Construction and Analysis of
  Systems. LNCS 8413, Springer Berlin Heidelberg, pp. 405--407, 2014.

%51
\bibitem{KahlonWG09}
Kahlon V., Wang C., Gupta A.:
\newblock {\em{Monotonic Partial Order Reduction: An Optimal Symbolic Partial Order Reduction Technique}}.
\newblock In: International Conference on Computer-Aided Verification, LNCS 5643, pp. 398--413, 2009.

%52
\bibitem{Alves15}
Alves E. , Cordeiro L., Lima Filho E.:
\newblock {\em{ Fault Localization in Multi-Threaded C Programs using Bounded Model Checking}}. 
\newblock In: Brazilian Symposium on Computing Systems Engineering, pp. 96-101, 2015.

%53
\bibitem{Garcia16}
Garcia M. , Sousa F., Cordeiro, L., Lima Filho E.: 
\newblock {\em{ ESBMC$^{QtOM}$: A Bounded Model Checking Tool to Verify Qt Applications}}. 
\newblock In: International SPIN symposium on Model Checking of Software (to appear), 2016.

%54
\bibitem{BeyerW15}
Beyer D., Dangl M., Dietsch D., Heizmann M., Stahlbauer A.:
\newblock {\em{ Witness validation and stepwise testification across software verifiers}}. 
\newblock In: ESEC/SIGSOFT Foundations of Software Engineering, pp. 721--733, 2015.

%55
\bibitem{RochaIFM12}
Rocha H., Barreto R., Cordeiro L., Dias Neto A.:
\newblock {\em{ Understanding Programming Bugs in ANSI-C Software Using Bounded Model Checking Counter-Examples}}. 
\newblock In: International Conference on Integrated Formal Methods, LNCS 7321, pp. 128-142, 2012.
